### 2016-02-03 chapters/abstract.tex
restructuring and changing for english style. starting to include a bibliography for references

In diesem Paper soll beschrieben werden, wie die Generierung eines Feature-Modells aus der Ordnerstruktur und den Konfigurationsdateien einer Produktlinie vorgenommen wird, hier am Beispiel von odoo.
Weiterhin wird der Vorgang der Konfiguration von Produktlinien betrachtet. Dazu wird zun\"achst untersucht, welche bestehenden Verfahren verwendet werden und ein Konzept, aufbauend auf dem Prinzip eines Fragebogens, entwickelt. Dabei soll auch die Erstellung eines solchen Fragebogens und die Beachtung einer eventuell gew\"unschten Reihenfolge in die Entwicklung des Konzeptes einflie\ss en.
Abschlie\ss end wird eine beispielhafte Umsetzung dieses Konzeptes in der IDE \textit{featureIDE} mit den zuvor ermittelten Anforderungen abgeglichen und bewertet.

>>>>

Variability management is an essential part of working on product lines.
This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
To further simplify the process of product configuration out of software product-lines, feature models are used to describe the set of features and constraints contained in a given software product-line. This paper proposes a method for automatically generating feature models out of descriptive files and naming conventions.

### 2016-02-03 chapters/concept.tex
restructuring and changing for english style. starting to include a bibliography for references

Schrittweise die Idee entwickeln und L\"osungswege f\"ur die gegebenen Probleme finden. Insbesondere auch verschiedene Ans\"atze vergleichen und getroffene Entscheidungen begr\"unden.

>>>>

\subsection{Problem statement}
Very high complexity of configuration due to many features and constraints. Domain knowledge is highly required to understand the given software product-line and being able to combine it's features to a valid configuration which satisfies the users needs.

\subsection{State of the art}
Compare the existing approaches to the stated problem and show why they are insufficient.

\subsection{Questionnaire Approach}
Use benefits of the existing approaches and overcome their shortcomings to solve the problem. State different variants and show the best one through comparison.

### 2016-02-03 chapters/conclusion.tex
restructuring and changing for english style. starting to include a bibliography for references

\subsection{Zusammenfassung}
Hier gibt es eine Zusammenfassung, der Arbeit. Darin flie\ss t insbesondere der gegangene Weg und die erlangten Erfahrungen ein. Insbesondere die gewonnenen Erkenntnisse in dieser Arbeit werden hervorgehoben und die Bewertung des entwickelten Konzeptes in wenigen S\"atzen zusammengefasst.

\subsection{Ausblick}
Hier werden die Fragen, die im Rahmen dieser Arbeit aufgeworfen wurden, konkretisiert und Themen f\"ur weitergehende Untersuchungen aufgez\"ahlt. Insbesondere Probleme, die das entwickelte Konzept nicht l\"osen kann sollen hervorgehoben werden (und warum) und erste Ans\"atze zu deren L\"osung vorgeschlagen werden.

>>>>

\subsection{Conclusion}
This is where the work is concluded. In this section there will be a description of the way we did things and the experiences we made during it. An emphasis will be on the insights and the findings from the scenarios will get outlined.

\subsection{Future Work}
Here will be a summary of the new questions that were raised in this work. Also there will be topics for further research. Particularly the problems we encountered and couldn't solve with our concept and why will be pointed out and first approaches will be suggested.

### 2016-02-03 chapters/intro.tex
restructuring and changing for english style. starting to include a bibliography for references

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{C}{onfiguration} is an essential part of working on product lines. This paper considers existing methods of configuration and tries to come up with a better alternative based on an approach with surveys.
Feature Models are vital tools for the configuration of product lines. This work aims at automatically generating feature models out of descriptive files and naming conventions, to simplify a big part of the configuration.

Anhand von vorangegangenen Untersuchungen zur Struktur von Frageb\"ogen wird anschlie\ss end ein Konzept entwickelt, das es Spezialisten erlaubt, ihre Dom\"anenkenntnisse in die Konfiguration einflie\ss en zu lassen, insbesondere in Bezug auf die Reihenfolge der zu treffenden Entscheidungen im Rahmen einer Konfiguration einer Produktlinie.

Abschlie\ss end wird das erarbeitete Konzept anhand einer beispielhaften Implementierung in die \textit{featureIDE} untersucht und insbesondere unter Anbetracht der eingangs ermittelten Anforderungen bewertet.

Contribution

@@

>>>>

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{V}{ariability} management is an essential part of working on product lines. There are several approaches trying to control the vast amount of product variants though configuration. This allows experts to apply their domain knowledge in order to a resulting product conforming to a users needs.

This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.

Feature Models are vital tools for the configuration of product lines in such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line. This work aims at automatically generating feature models out of descriptive files and naming conventions, to simplify a big part of the configuration.

\section*{Contribution}

@@

This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy to create citations.
